Target Markdown

### 2024-03-07 _targets.Rmd
Option to remove or kill disconnected species + fix h

```{targets all-analysis}
library(tarchetypes)
tar_map(
  values = map_tibble,
  names = names,
  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
  tar_target(sim_fw, readRDS(sim_files)),
  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
  tar_target(sem_simplified_eff, { readRDS(sem_simplified_eff_file) }),
  tar_target(sem_simplified_collinearity_file, here::here("data", paste0("sem_simplified_collinearity_", names)), format = "file"),
  tar_target(sem_simplified_collinearity, { readRDS(sem_simplified_collinearity_file) }),
  tar_target(sem_simplified_rsquared_file, here::here("data", paste0("sem_simplified_rsquared_", names)), format = "file"),
  tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

@@

```{r debug, eval = FALSE}
tar_load(sim_fw)
ti <- sim_fw %>%
  mutate(across(c(stab_com, richness), log)) %>%
  mutate(across(c(sim_id, fw_id), as.factor)) %>%
  mutate(
    across(c(stab_com, richness,
        env_stoch, resp_div, Z,
        ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
      ~scale(.x)[, 1])
  )
tar_load(stab_com_part_var)
tu <- map(stab_com_part_var,
  ~glmmTMB(formula_stab_fw_model(
      resp = .x,
      rand_effect = TRUE,
      term_to_del = "richness : resp_div : Z +"
      ),
    data = ti
    ))
```

>>>>

```{targets all-analysis}
library(tarchetypes)
tar_map(
  values = map_tibble,
  names = names,
  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
  tar_target(sim_fw, readRDS(sim_files)),
  tar_target(sem_simplified_file, here::here("data", paste0("sem_simplified_", names)), format = "file"),
  tar_target(sem_simplified, { readRDS(sem_simplified_file) }),
  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
  tar_target(sem_simplified_eff, { readRDS(sem_simplified_eff_file) }),
  tar_target(sem_simplified_collinearity_file, here::here("data", paste0("sem_simplified_collinearity_", names)), format = "file"),
  tar_target(sem_simplified_collinearity, { readRDS(sem_simplified_collinearity_file) }),
  tar_target(sem_simplified_rsquared_file, here::here("data", paste0("sem_simplified_rsquared_", names)), format = "file"),
  tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

@@

```{r debug, eval = FALSE}
tar_load(sim_fw)
tar_load(c(sim_fw_no_rerun,
    sim_fw_rerun,
    sim_fw_no_rerun_short,
    sim_fw_no_rerun_no_disconnected,
    sim_fw_non_allo_no_rerun))
tar_load(c(
    sem_simplified_no_rerun,
    sem_simplified_rerun,
    sem_simplified_no_rerun_short,
    sem_simplified_no_rerun_no_disconnected,
    sem_simplified_non_allo_no_rerun
    ))
```
